Download data

### 2023-12-06 scripts/download_dependent_variables.Rmd
AIM import for presence

@@

@@

## we will add on USDA codes so we can interface with AIM data. 
symbols <- read.csv('../data/raw/USDA_PLANTS.csv') %>% 
  right_join(., targets, by = c('' = 'taxon'))

@@

# for some strange reason this not exactly working! a weird /gdb is being tagged
# onto the end of it... we can manually specify the data beneath
st_layers(dsn = p1)

AIM_points <- st_read(dsn = p1, 
        layer = 'TerrADat', quiet = T) %>%
#  filter(State %in% c('NV', 'OR', 'CA', 'ID', 'UT')) %>% 
  select(PrimaryKey, geometry = Shape) %>% 
  st_transform(5070)

# AIM_points <- AIM_points[st_covered_by(AIM_points, field_off) %>% lengths > 0,]

spp_richness <- st_read(dsn = p1, 
        layer = 'tblSpecRichDetail', quiet = T) %>% 
  select(SpeciesList, PrimaryKey) %>% 
  right_join(AIM_points, by = 'PrimaryKey')

spp_found <- inner_join(target_taxa_lkp, spp_richness, 
                        by = c('USDA.Code' = 'SpeciesList')) %>% 
  select(species, PrimaryKey, geometry) %>% 
  st_as_sf()

spp_occurrences <- bind_rows(spp_found, pub_presence) %>% 
  arrange(species) %>% 
  relocate(c('year', 'date'), .before = geometry) %>% 
  mutate(species = str_trim(species)) %>% 
  filter(!species %in% c('Artemisia tridentata',
                         'Elymus elymoides',
                         'Poa secunda'))

>>>>

targets %>% 
  group_by(symbol, taxon) %>% 
  count()

@@

target_symbols <- targets %>% 
  pull(symbol) %>% 
  unique()

@@

@@

st_layers(dsn = p1)

AIM_points <- st_read(dsn = p1, 
        layer = 'TerrADat', quiet = T) %>%
  select(PrimaryKey, DateVisited, geometry = Shape) %>% 
  st_transform(5070)

spp_richness <- st_read(dsn = p1, 
        layer = 'tblSpecRichDetail', quiet = T) %>% 
  select(SpeciesList, PrimaryKey) %>% 
  filter(SpeciesList %in% target_symbols) %>% 
  right_join(AIM_points, by = 'PrimaryKey') %>% 
  st_as_sf()  %>% 
  mutate(YearSampled = gsub('-.*$', '', DateVisited), .before = geometry) %>% 
  select(-DateVisited) %>% 
  arrange(SpeciesList) %>% 
  right_join(., select(targets, taxon, symbol) %>% 
               distinct(), by = c('SpeciesList' = 'symbol' ))

st_write(spp_richness, '../data/raw/occurrence/AIM/AIM_records.shp')

rm(p1, AIM_points)
```
